---
title: "1_TwitterScrape"
author: "Ursula Widocki and Katherine Cyr"
date: "12/13/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# I. Overview and Motivation:

#### Historical Context: 

Trump impeachment hearings, Trump allegedly withheld US aid to Ukraine unless president of Ukraine investigated Joe Biden's son (so we expect many Tweets related to Joe Biden & impeachment inquiry) [https://www.npr.org/2019/10/28/771287237/trump-impeachment-inquiry-a-guide-to-key-people-facts-and-documents]
Joe Biden and Elizabeth Warren previously top candidates in Iowa polls, recently surpassed by Pete Buttigeg [https://www.nytimes.com/2019/11/16/us/politics/iowa-poll-democrats.html]

#### Debate info:

hosted on 11/20/2019 at 8pm EST 
held in Atlanta, GA
hosted by MSNBC
all female journalists moderating the debate: Andrea Mitchell, Rachel Maddow, Kristen Welker & Ashley Parker

#### Candidate profiles:

Former Vice President Joe Biden
Sen. Cory Booker (New Jersey)
Mayor Pete Buttigieg (South Bend, Indiana)
Rep. Tulsi Gabbard (Hawaii)
Sen. Kamala Harris (California)
Sen. Amy Klobuchar (Minnesota)
Sen. Bernie Sanders (Vermont)
Billionaire Tom Steyer
Sen. Elizabeth Warren (Massachusetts)
Entrepreneur Andrew Yang

# II. Related Work:

FiveThirtyEight: Nate Silver of FiveThirtyEight gained much attention when he aggregated many political polls and gained more accurate insight than any of the polls individually. Now, FiveThrityEight is a webiste that focuses on using statistical analysis (hard numbers) to tell compelling stories about elections, politics, sports, science, economicsand sports blogging.

FiveThirtyEight inspired us to analyze the Democratic Party Primary Presidential Debate in a creative way using Twitter data, Google Trends data, and the debate transcript to explore performance in the president race to win the primaries.

# III. Initial Questions: 

Assessing debate performance using Twitter reactions
Approximate time stamps on debate transcript 
Calculate length of debate (we expect two hours, account for commercials)
Words have same time unit
Map tweets to time stamps
Calculate and plot frequency for each candidate
Map points on frequency plot to debate transcript timestamp and word cloud of tweets
Explore connectivity and frequency of hashtags

# IV. Data:

Data collection:
 
source: Twitter, debate transcript
scraping method
cleanup
Important R packages:
Wordcloud
Igraph (if we do network analysis)
StringR
TwitteR
GGplot2
Dplyr 
networkD3

# Notes

There are many Trump mentions in the data, so Twitter’s reaction to the debate may not be representative of Democratic voters’ reaction to the debate. 
Computational issues: the way tweets were scraped may cause the sample to not be representative of the populations

----------------------------------------------------------------------------------------------------------------

The following code was run in an R script to scrape tweets from Twitter. It is put into chunks to make it easier to read and follow but commented out so that this file can be knit

```{r, include = FALSE}
# packages to import
#library(twitteR)
#library(httr)
#library(ROAuth)
#library(igraph)
#library(stringr)
#library(dplyr)

```

In order to scrape data from Twitter, we used Kat's Twitter developer account to access the tweets. The following allows her to log in to access the data:

```{r, include= FALSE}
# Assuming that we've gotten our authentication information, we can now build up our login credentials
# personal login information has been omitted

#consumerKey <- ""
#consumerSecret <- ""
#ccessToken<-  ""
#accessSecret<- ""

#reqURL <- ""
#accessURL <- ""
#authURL <- ""

# We put them into one piece that will log us in
#twitCred <- OAuthFactory$new(consumerKey=consumerKey, consumerSecret=consumerSecret, requestURL=reqURL, #accessURL=accessURL, authURL=authURL)

# But now we need to do something called a handshake to comlplete the login process
#twitCred$handshake()
# Now follow your browser until you get to a large number and paste it where it asks for it in the console

# Let's save this so we don't have to redo it all the time for different R scripts
#save(twitCred, file="credentials.RData")




# So now let's log in
## To do so, we're going to need to go find something another
#setup_twitter_oauth("",
                    #"",
                    #"",
                    #"")


```

The next chunk has lines we used to run in order to collect tweets during the debate

```{r, include= FALSE}
#tweetList <- searchTwitteR(" \"#DemDebate\" OR \"#JoeBiden\" OR \"#JoeBiden2020\" OR  \"#PeteButtigieg\" OR \"#PeteForPresident\" OR \"#ElizabethWarren\"  OR \"#Warren2020\" OR \"#BernieSanders\" OR \"#Bernie2020\" ", n=1000)

#tweetList1 <- searchTwitteR(" \"#DemDebate\" OR \"#JoeBiden\" OR \"#JoeBiden2020\" OR  \"#PeteButtigieg\" OR \"#PeteForPresident\" OR \"#ElizabethWarren\"  OR \"#Warren2020\" OR \"#BernieSanders\" OR \"#Bernie2020\" ", n=1000)

#tweetList2 <- searchTwitteR(" \"#DemDebate\" OR \"#JoeBiden\" OR \"#JoeBiden2020\" OR  \"#PeteButtigieg\" OR \"#PeteForPresident\" OR \"#ElizabethWarren\"  OR \"#Warren2020\" OR \"#BernieSanders\" OR \"#Bernie2020\" ", n=1000)

#tweetList3 <- searchTwitteR(" \"#DemDebate\" OR \"#JoeBiden\" OR \"#JoeBiden2020\" OR  \"#PeteButtigieg\" OR \"#PeteForPresident\" OR \"#ElizabethWarren\"  OR \"#Warren2020\" OR \"#BernieSanders\" OR \"#Bernie2020\" ", n=1000)

#tweetList4 <- searchTwitteR(" \"#DemDebate\" OR \"#JoeBiden\" OR \"#JoeBiden2020\" OR  \"#PeteButtigieg\" OR \"#PeteForPresident\" OR \"#ElizabethWarren\"  OR \"#Warren2020\" OR \"#BernieSanders\" OR \"#Bernie2020\" ", n=10000)

#tweetList5<- searchTwitteR(" \"#DemDebate\" OR \"#JoeBiden\" OR \"#JoeBiden2020\" OR  \"#PeteButtigieg\" OR \"#PeteForPresident\" OR \"#ElizabethWarren\"  OR \"#Warren2020\" OR \"#BernieSanders\" OR \"#Bernie2020\" ", n=10000)

#tweetList6 <- searchTwitteR(" \"#DemDebate\" OR \"#JoeBiden\" OR \"#JoeBiden2020\" OR  \"#PeteButtigieg\" OR \"#PeteForPresident\" OR \"#ElizabethWarren\"  OR \"#Warren2020\" OR \"#BernieSanders\" OR \"#Bernie2020\" ", n=10000)

#tweetList7 <- searchTwitteR(" \"#DemDebate\" OR \"#JoeBiden\" OR \"#JoeBiden2020\" OR  \"#PeteButtigieg\" OR \"#PeteForPresident\" OR \"#ElizabethWarren\"  OR \"#Warren2020\" OR \"#BernieSanders\" OR \"#Bernie2020\" ", n=10000)

#tweetList8 <- searchTwitteR(" \"#DemDebate\" OR \"#JoeBiden\" OR \"#JoeBiden2020\" OR  \"#PeteButtigieg\" OR \"#PeteForPresident\" OR \"#ElizabethWarren\"  OR \"#Warren2020\" OR \"#BernieSanders\" OR \"#Bernie2020\" ", n=10000)

#tweetList9 <- searchTwitteR(" \"#DemDebate\" OR \"#JoeBiden\" OR \"#JoeBiden2020\" OR  \"#PeteButtigieg\" OR \"#PeteForPresident\" OR \"#ElizabethWarren\"  OR \"#Warren2020\" OR \"#BernieSanders\" OR \"#Bernie2020\" ", n=10000)

#tweetList10 <- searchTwitteR(" \"#DemDebate\" OR \"#JoeBiden\" OR \"#JoeBiden2020\" OR  \"#PeteButtigieg\" OR \"#PeteForPresident\" OR \"#ElizabethWarren\"  OR \"#Warren2020\" OR \"#BernieSanders\" OR \"#Bernie2020\" ", n=10000)

#tweetList11 <- searchTwitteR(" \"#DemDebate\" OR \"#JoeBiden\" OR \"#JoeBiden2020\" OR  \"#PeteButtigieg\" OR \"#PeteForPresident\" OR \"#ElizabethWarren\"  OR \"#Warren2020\" OR \"#BernieSanders\" OR \"#Bernie2020\" ", n=10000)

#tweetList12 <- searchTwitteR(" \"#DemDebate\" OR \"#JoeBiden\" OR \"#JoeBiden2020\" OR  \"#PeteButtigieg\" OR \"#PeteForPresident\" OR \"#ElizabethWarren\"  OR \"#Warren2020\" OR \"#BernieSanders\" OR \"#Bernie2020\" ", n=10000)

#tweetList13 <- searchTwitteR(" \"#DemDebate\" OR \"#JoeBiden\" OR \"#JoeBiden2020\" OR  \"#PeteButtigieg\" OR \"#PeteForPresident\" OR \"#ElizabethWarren\"  OR \"#Warren2020\" OR \"#BernieSanders\" OR \"#Bernie2020\" ", n=10000)

#tweetList14 <- searchTwitteR(" \"#DemDebate\" OR \"#JoeBiden\" OR \"#JoeBiden2020\" OR  \"#PeteButtigieg\" OR \"#PeteForPresident\" OR \"#ElizabethWarren\"  OR \"#Warren2020\" OR \"#BernieSanders\" OR \"#Bernie2020\" ", n=10000)

#tweetList16 <- searchTwitteR(" \"#DemDebate\" OR \"#JoeBiden\" OR \"#JoeBiden2020\" OR  \"#PeteButtigieg\" OR \"#PeteForPresident\" OR \"#ElizabethWarren\"  OR \"#Warren2020\" OR \"#BernieSanders\" OR \"#Bernie2020\" ", n=10000, since = "2019-11-21")
```

The data were converted into data frames and saved as CSVs

```{r, include = FALSE}
#tweetDF <- twListToDF(tweetList)
#tweetDF1 <- twListToDF(tweetList1)
#tweetDF2 <- twListToDF(tweetList2)
#tweetDF3 <- twListToDF(tweetList3)
#tweetDF4 <- twListToDF(tweetList4)
#tweetDF5 <- twListToDF(tweetList5)
#tweetDF6 <- twListToDF(tweetList6)
#tweetDF7 <- twListToDF(tweetList7)
#tweetDF8 <- twListToDF(tweetList8)
#tweetDF9 <- twListToDF(tweetList9)
#tweetDF10 <- twListToDF(tweetList10)
#tweetDF11 <- twListToDF(tweetList11)
#tweetDF12 <- twListToDF(tweetList12)
#tweetDF13 <- twListToDF(tweetList13)
#tweetDF14 <- twListToDF(tweetList14)
#tweetDF16 <- twListToDF(tweetList16)

#write.csv(tweetDF1, "tweetDF1.csv")
#write.csv(tweetDF2, "tweetDF2.csv")
#write.csv(tweetDF3, "tweetDF3.csv")
#write.csv(tweetDF4, "tweetDF4.csv")
#write.csv(tweetDF5, "tweetDF5.csv")
#write.csv(tweetDF6, "tweetDF6.csv")
#write.csv(tweetDF7, "tweetDF7.csv")
#write.csv(tweetDF8, "tweetDF8.csv")
#write.csv(tweetDF9, "tweetDF9.csv")
#write.csv(tweetDF10, "tweetDF10.csv")
#write.csv(tweetDF11, "tweetDF11.csv")
#write.csv(tweetDF12, "tweetDF12.csv")
#write.csv(tweetDF13, "tweetDF13.csv")
#write.csv(tweetDF14, "tweetDF14.csv")
#write.csv(tweetDF16, "tweetDF16.csv")
#write.csv(tweetDF, "tweetDF_0.csv")
```











